New lower bounds for Schur and weak Schur numbers

### 2021-05-07 article/schur.tex
Changement de titres
jolis tableaux :'(
anglais + erreurs

\section{Schur numbers}
\label{Schur}

@@

\begin{definition}
A SF-template with length \(p\) and \(n\) colors is defined as a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets 
\(A_1, A_2, ..., A_n\) verifying:
\[
\forall i \in [\![1, n-1]\!], \forall (x,y) \in A_i^2, x+y > p
\Longrightarrow x+y-p \notin A_i
\]
\end{definition}

@@

\begin{proposition}
	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the maximal lenght of a SF-template with \(n\) colors. 
	\(S^+(n)\) is well defined and verifies:
	\[
	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n)
	\]
\end{proposition}

\begin{proof}[\textsc{Proof.}]
The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
fact that a SF-template with length \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets.
\end{proof}

@@

\begin{theorem}
	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with lenght \(p\) and \(k+1\) colors 
	and a partition of \([\![1,q]\!]\) into \(n\) sum-free subsets then there exists a partition of \([\![1,pq+m_{k+1}
	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{k+1}\) is the minimum of the special subset in the \(SF\)-template.
\end{theorem}

@@

\begin{center}
\textbf{Abbott and Hanson's construction}
\end{center}

\[
\begin{array}{|*{9}{c|}}
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{cyan} 5 & 
	\cellcolor{cyan} 6 & \cellcolor{cyan} 7 & \cellcolor{cyan} 8 & \cellcolor{cyan} 9\\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & 
	\cellcolor{yellow} 15 & \cellcolor{yellow} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & 
	\cellcolor{yellow} 24 & \cellcolor{yellow} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{cyan} 32 & 
	\cellcolor{cyan} 33 & \cellcolor{cyan} 34 & \cellcolor{cyan} 35 & \cellcolor{cyan} 36 \\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
	\cline{1-4}
\end{array}
\]

\begin{center}
\begin{tabular}{c c}
	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
	\begin{tabular}{|*{9}{c|}}
		\hline 
		\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{gray!40} 5 & 
		\cellcolor{gray!40} 6 & \cellcolor{gray!40} 7 & \cellcolor{gray!40} 8 & \cellcolor{gray!40} 9 \\
		\hline
	\end{tabular} &
	\begin{tabular}{|*{4}{c|}}
		\hline 
		\cellcolor{cyan} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{cyan} 4 \\
		\hline
	\end{tabular}
\end{tabular}
\end{center}

@@

\begin{center}
\textbf{SF-template construction}
\end{center}

\[
\begin{array}{|*{9}{c|}}
	\hline
	\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{cyan} 5 & 
	\cellcolor{cyan} 6 & \cellcolor{red} 7 & \cellcolor{cyan} 8 & \cellcolor{cyan} 9\\
	\hline
	\cellcolor{red} 10 & \cellcolor{green} 11 & \cellcolor{green} 12 & \cellcolor{red} 13 & \cellcolor{yellow} 14 & 
	\cellcolor{yellow} 15 & \cellcolor{red} 16 & \cellcolor{yellow} 17 & \cellcolor{yellow} 18\\
	\hline
	\cellcolor{red} 19 & \cellcolor{green} 20 & \cellcolor{green} 21 & \cellcolor{red} 22 & \cellcolor{yellow} 23 & 
	\cellcolor{yellow} 24 & \cellcolor{red} 25 & \cellcolor{yellow} 26 & \cellcolor{yellow} 27\\
	\hline
	\cellcolor{red} 28 & \cellcolor{green} 29 & \cellcolor{green} 30 & \cellcolor{red} 31 & \cellcolor{cyan} 32 & 
	\cellcolor{cyan} 33 & \cellcolor{red} 34 & \cellcolor{cyan} 35 & \cellcolor{cyan} 36 \\
	\hline
	\cellcolor{red} 37 & \cellcolor{green} 38 & \cellcolor{green} 39 & \cellcolor{red} 40 \\
	\cline{1-4}
\end{array}
\]

\begin{center}
\begin{tabular}{c c}
	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
	\begin{tabular}{|*{9}{c|}}
		\hline 
		\cellcolor{red} 1 & \cellcolor{green} 2 & \cellcolor{green} 3 & \cellcolor{red} 4 & \cellcolor{gray!40} 5 & 
		\cellcolor{gray!40} 6 & \cellcolor{red} 7 & \cellcolor{gray!40} 8 & \cellcolor{gray!40} 9 \\
		\hline
	\end{tabular} &
	\begin{tabular}{|*{4}{c|}}
		\hline 
		\cellcolor{cyan} 1 & \cellcolor{yellow} 2 & \cellcolor{yellow} 3 & \cellcolor{cyan} 4 \\
		\hline
	\end{tabular}
\end{tabular}
\end{center}

@@

\begin{proof}[\textsc{Proof.}]
Denote by \(f\) the colouring associated to the \(SF\)-template of lenght \(p\) and \(g\) the one associated 
to the sum-free partition of \([\![1,q]\!]\); where \(f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!]\) and 
\(g : [\![1,q]\!] \longrightarrow [\![1,n]\!]\).

@@

\begin{proposition}
Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a colouring associated to a SF-template of length \(p\) with \(k+1\) 
colors. Let \(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a colouring \(g\) of 
\([\![1, b]\!]\) with \(k+1\) colors such that:

@@

Then, for every \(n \in \mathbb{N}^*\), by using on the last row the colouring \(i \longmapsto g(i - p S(n))\), we have
\[ S(n+k) \geqslant S^+(k+1)S(n) + b\]
\end{proposition}

This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the colouring of the last 
row can be weakened.

@@

\begin{theorem}
	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template of \(k+1\) colors and lenght \(p\),
	and \(SF\)-template of \(n\) color and lenght \(q\), then there exists \(SF\)-template of \((n+k)\) and lenght \(pq\).
\end{theorem}

@@

\subsection{New lower bounds for Schur numbers}

@@

\par
Here are the best inequalities on Schur numbers so far (the templates corresponding to the third, fourth and fifth 
inequalities can be found in the appendix):
\[
\begin{array}{r r r r r}
	S(n + 1) & \geqslant & 3 S(n) & + & 1 \\
	S(n + 2) & \geqslant & 9 S(n) & + & 4 \\
	S(n + 3) & \geqslant & 33 S(n) & + & 6 \\
	S(n + 4) & \geqslant & 111 S(n) & + & 43 \\
	S(n + 5) & \geqslant & 380 S(n) & + & 148 \\
	S(n + 6) & \geqslant & 1140 S(n) & + & 528 \\
\end{array}
\]

@@

\par
The first 3 inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
likely not optimal but should not be too far from the optimal. 
Finally, the sixth one is obtained by combining (see below) the SF-template of length 380 and the one of length 3. 
Although we could not find a better SF-template with 7 colors, the last inequality is definetely very far from the 
optimal value. One may try to seek better templates by constraining less the search space and by using 
Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.

@@

\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	\(n\) & 8 & 9 & 10 & 11 \\
	\hline
	\(33S(n-3) + 6 \) & \cellcolor{yellow} 5286 & 17694 & 55446 & 174444\\
	\hline
	\(111S(n-4) + 43 \) & 4927 & \cellcolor{yellow} 17803 & 59539 & 186523\\
	\hline
	\(380S(n-5) + 148 \) & 5088 & 16868 & \cellcolor{yellow} 60948 & \cellcolor{yellow} 203828 \\
	\hline
	\(1140S(n-6) + 528 \) & 5088 & 15348 & 50688 & 182928\\
	\hline
	\hline
	\(n\) & 12 & 13 & 14 & 15 \\
	\hline
	\(33S(n-3) + 6 \) & 587505 & \cellcolor{yellow} 2011290 & 6726330 & 21072090\\
	\hline
	\(111S(n-4) + 43 \) & 586789 & 1976176 & 6765271 & 22624951 \\
	\hline
\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\\hline
	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\
	\hline
\end{tabular}
\end{center}

>>>>

\section{Templates for Schur numbers}
\label{Schur}

@@

\begin{definition}
A SF-template with width \(p\) and \(n\) colors is defined as a partition of \( [\![1,p]\!]\) into \(n\) sum-free subsets 
\(A_1, A_2, ..., A_n\) verifying:
\[
\forall i \in [\![1, n-1]\!], \forall (x,y) \in A_i^2, x+y > p
\Longrightarrow x+y-p \notin A_i
\]
\end{definition}

@@

\begin{proposition}
	Let \(n \in [\![2, +\infty[\![\). We define \(S^+(n)\) as the maximal width of a SF-template with \(n\) colors. 
	\(S^+(n)\) is well defined and verifies:
	\[
	2S(n-1)+1 \leqslant S^+(n) \leqslant S(n)
	\]
\end{proposition}

\begin{proof}[\textsc{Proof.}]
The lower bound comes from Abbott and Hanson's construction. The upper bound comes from the 
fact that a SF-template with width \(p\) and \(n\) colors is also a partition of \([\![1, p]\!]\) into \(n\) sum-free subsets.
\end{proof}

@@

\begin{theorem}
	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with width \(p\) and \(k+1\) colors 
	and a partition of \([\![1,q]\!]\) into \(n\) sum-free subsets then there exists a partition of \([\![1,pq+m_{k+1}
	-1]\!]\) into \(n+k\) sum-free subsets. \(m_{k+1}\) is the minimum of the special subset in the \(SF\)-template.
\end{theorem}

@@

\renewcommand{\arraystretch}{1.7}

\begin{center}
\setlength{\tabcolsep}{1.5ex}

\textbf{Abbott and Hanson's construction}
\vspace{1.7ex}

\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
\CodeBefore
	\cellcolor{red}{1-1}
	\cellcolor{green}{1-2}
	\cellcolor{green}{1-3}
	\cellcolor{red}{1-4}
	\cellcolor{cyan}{1-5}
	\cellcolor{cyan}{1-6}
	\cellcolor{cyan}{1-7}
	\cellcolor{cyan}{1-8}
	\cellcolor{cyan}{1-9}
	\cellcolor{red}{2-1}
	\cellcolor{green}{2-2}
	\cellcolor{green}{2-3}
	\cellcolor{red}{2-4}
	\cellcolor{yellow}{2-5}
	\cellcolor{yellow}{2-6}
	\cellcolor{yellow}{2-7}
	\cellcolor{yellow}{2-8}
	\cellcolor{yellow}{2-9}
	\cellcolor{red}{3-1}
	\cellcolor{green}{3-2}
	\cellcolor{green}{3-3}
	\cellcolor{red}{3-4}
	\cellcolor{yellow}{3-5}
	\cellcolor{yellow}{3-6}
	\cellcolor{yellow}{3-7}
	\cellcolor{yellow}{3-8}
	\cellcolor{yellow}{3-9}
	\cellcolor{red}{4-1}
	\cellcolor{green}{4-2}
	\cellcolor{green}{4-3}
	\cellcolor{red}{4-4}
	\cellcolor{cyan}{4-5}
	\cellcolor{cyan}{4-6}
	\cellcolor{cyan}{4-7}
	\cellcolor{cyan}{4-8}
	\cellcolor{cyan}{4-9}
	\cellcolor{red}{5-1}
	\cellcolor{green}{5-2}
	\cellcolor{green}{5-3}
	\cellcolor{red}{5-4}
\Body
	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
	37 & 38 & 39 & 40 \\
\end{NiceTabular}

\vspace{1ex}
\setlength{\tabcolsep}{2ex}

\begin{tabular}{c c}
	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
	\begin{NiceTabular}{|*{9}{c|}}[standard-cline,hlines]
	\CodeBefore 
		\cellcolor{red}{1-1}
		\cellcolor{green}{1-2}
		\cellcolor{green}{1-3}
		\cellcolor{red}{1-4}
		\cellcolor{gray!40}{1-5}
		\cellcolor{gray!40}{1-6}
		\cellcolor{gray!40}{1-7}
		\cellcolor{gray!40}{1-8}
		\cellcolor{gray!40}{1-9}
	\Body
		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
	\end{NiceTabular} &
	\begin{NiceTabular}{|*{4}{c|}}[standard-cline,hlines]
	\CodeBefore
		\cellcolor{cyan}{1-1}
		\cellcolor{yellow}{1-2}
		\cellcolor{yellow}{1-3}
		\cellcolor{cyan}{1-4}
	\Body
		1 & 2 & 3 & 4 \\
	\end{NiceTabular}
\end{tabular}

\setlength{\tabcolsep}{6pt}
\end{center}

@@

\begin{center}
\setlength{\tabcolsep}{1.5ex}

\textbf{SF-template construction}
\vspace{1.7ex}

\begin{NiceTabular}{|*{9}{c|}}[corners=SE,standard-cline,hlines]
\CodeBefore
	\cellcolor{red}{1-1}
	\cellcolor{green}{1-2}
	\cellcolor{green}{1-3}
	\cellcolor{red}{1-4}
	\cellcolor{cyan}{1-5}
	\cellcolor{cyan}{1-6}
	\cellcolor{red}{1-7}
	\cellcolor{cyan}{1-8}
	\cellcolor{cyan}{1-9}
	\cellcolor{red}{2-1}
	\cellcolor{green}{2-2}
	\cellcolor{green}{2-3}
	\cellcolor{red}{2-4}
	\cellcolor{yellow}{2-5}
	\cellcolor{yellow}{2-6}
	\cellcolor{red}{2-7}
	\cellcolor{yellow}{2-8}
	\cellcolor{yellow}{2-9}
	\cellcolor{red}{3-1}
	\cellcolor{green}{3-2}
	\cellcolor{green}{3-3}
	\cellcolor{red}{3-4}
	\cellcolor{yellow}{3-5}
	\cellcolor{yellow}{3-6}
	\cellcolor{red}{3-7}
	\cellcolor{yellow}{3-8}
	\cellcolor{yellow}{3-9}
	\cellcolor{red}{4-1}
	\cellcolor{green}{4-2}
	\cellcolor{green}{4-3}
	\cellcolor{red}{4-4}
	\cellcolor{cyan}{4-5}
	\cellcolor{cyan}{4-6}
	\cellcolor{red}{4-7}
	\cellcolor{cyan}{4-8}
	\cellcolor{cyan}{4-9}
	\cellcolor{red}{5-1}
	\cellcolor{green}{5-2}
	\cellcolor{green}{5-3}
	\cellcolor{red}{5-4}
\Body
	1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
	10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 \\
	19 & 20 & 21 & 22 & 23 & 24 & 25 & 26 & 27 \\
	28 & 29 & 30 & 31 & 32 & 33 & 34 & 35 & 36 \\
	37 & 38 & 39 & 40 \\
\end{NiceTabular}

\vspace{1ex}
\setlength{\tabcolsep}{2ex}

\begin{tabular}{c c}
	\textbf{Corresponding SF-template} & \textbf{Corresponding sum-free partition} \\
	\begin{NiceTabular}{|*{9}{c|}}[standard-cline,hlines]
	\CodeBefore 
		\cellcolor{red}{1-1}
		\cellcolor{green}{1-2}
		\cellcolor{green}{1-3}
		\cellcolor{red}{1-4}
		\cellcolor{gray!40}{1-5}
		\cellcolor{gray!40}{1-6}
		\cellcolor{red}{1-7}
		\cellcolor{gray!40}{1-8}
		\cellcolor{gray!40}{1-9}
	\Body
		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\
	\end{NiceTabular} &
	\begin{NiceTabular}{|*{4}{c|}}[standard-cline,hlines]
	\CodeBefore
		\cellcolor{cyan}{1-1}
		\cellcolor{yellow}{1-2}
		\cellcolor{yellow}{1-3}
		\cellcolor{cyan}{1-4}
	\Body
		1 & 2 & 3 & 4 \\
	\end{NiceTabular}
\end{tabular}

\setlength{\tabcolsep}{6pt}
\end{center}

\resetarraystretch

@@

\begin{proof}[\textsc{Proof.}]
Denote by \(f\) the coloring associated to the \(SF\)-template with width \(p\) and \(g\) the one associated 
to the sum-free partition of \([\![1,q]\!]\); where \(f : [\![1,p]\!] \longrightarrow [\![1,k+1]\!]\) and 
\(g : [\![1,q]\!] \longrightarrow [\![1,n]\!]\).

@@

\begin{proposition}
Let \((k, p) \in \mathbb{N}^*)^2\) and let \(f\) be a coloring associated to a SF-template with width \(p\) and \(k+1\) 
colors. Let \(b \in \mathbb{N}\) (\(b = m_{k+1} - 1\) works) and assume there there exists a coloring \(g\) of 
\([\![1, b]\!]\) with \(k+1\) colors such that:

@@

Then, for every \(n \in \mathbb{N}^*\), by using on the last row the coloring \(i \longmapsto g(i - p S(n))\), we have
\[ S(n+k) \geqslant S^+(k+1)S(n) + b\]
\end{proposition}

This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the coloring of the last 
row can be weakened.

@@

\begin{theorem}
	Let \((n,k), (p,q) \in (\mathbb{N}^*)^2\). If there exists a \(SF\)-template with and \(p\) and \(k+1\) colors,
	and a \(SF\)-template with width \(q\) and \(n\) colors, then there exists \(SF\)-template with width \(pq\) and \((n+k)\).
\end{theorem}

@@

\subsection{Inequalities and new lower bounds for Schur numbers}

@@

\par
Here are the best inequalities on Schur numbers so far (the templates corresponding to the third, fourth and fifth 
inequalities can be found in the appendix):
\[
\begin{array}{r r r r r}
	S(n + 1) & \geqslant & 3 S(n) & + & 1 \\
	S(n + 2) & \geqslant & 9 S(n) & + & 4 \\
	S(n + 3) & \geqslant & 33 S(n) & + & 6 \\
	S(n + 4) & \geqslant & 111 S(n) & + & 43 \\
	S(n + 5) & \geqslant & 380 S(n) & + & 148 \\
	S(n + 6) & \geqslant & 1\,140 S(n) & + & 528 \\
\end{array}
\]

@@

\par
The first 3 inequalities are optimal. The fourth one is optimal among symmetric SF-templates whose special color is 
the last in the order of apparition (and with a multiplicative factor less than or equal to 118). The fifth one is most 
likely not optimal but should not be too far from the optimal. 
Finally, the sixth one is obtained by combining (see below) the SF-template with width 380 and the one with width 3. 
Although we could not find a better SF-template with 7 colors, the last inequality is definetely very far from the 
optimal value. One may try to seek better templates by constraining less the search space and by using 
Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the suject of a future work.

@@

\renewcommand{\arraystretch}{0.2}

\[
\begin{array}{c}
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 8 & 9 & 10 & 11 \\
		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,446 & 174\,444 \\
		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 186\,523 \\
		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
		1\,140 \, S(n-6) + 528 & 5\,088 & 15\,348 & 50\,688 & 182\,928 \\
	\end{NiceArray}
	\\ \\
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-3}
		\cellcolor{yellow}{4-2}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,072\,090 \\
		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
		380 \, S(n-5) + 148 & 638\,548 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
		1\,140 \, S(n-6) + 528 & 611\,568 & 1\,915\,728 & 6\,026\,568 & 20\,295\,948 \\
	\end{NiceArray}
\end{array}
\]

\resetarraystretch

### 2021-05-07 article/search_space.tex
Changement de titres
sperateur miliers + jolis tableaux (1/2)
anglais + erreurs

\subsection{Former assumption appears to be wrong}

@@

\par
For every weakly sum-free colouring \(f\) of \([\![1,65]\!]\) with 4 colors, the sequence \(f(1), f(2), f(3), ...\) always
starts with the following subsequence 1121222133. Then 11 is always
either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which
subset it can appear.
By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear
in a weakly sum-free
partition of \([\![1,185]\!]\) which starts with a weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding
these constraints to the
formula corresponding to the above theorem gives additional information to the SAT solver without losing in generality.

@@

\subsection{Weak Schur number five}

@@

>>>>

\subsection{Limitation of the former assumption}

@@

\par
For every weakly sum-free coloring \(f\) of \([\![1,65]\!]\) with 4 colors, the sequence \(f(1), f(2), f(3), ...\) always
starts with the following subsequence 1121222133. Then 11 is always
either in subset 1 or 3, 12 is always in subset 3 and so on. For every integer in \([\![1,65]\!]\), we computed in which
subset it can appear.
By using this constraints, we could then compute for every integer in \([\![1,185]\!]\), in which subset it can appear
in a weakly sum-free
partition of \([\![1,185]\!]\) which starts with a weakly sum-free partition of \([\![1,65]\!]\) in 4 subsets. Adding
these constraints to the
formula corresponding to the above theorem gives additional information to the SAT solver without losing in generality.

@@

\subsection{Investigating weak Schur number five}

@@

\resetarraystretch
\setlength{\tabcolsep}{6pt}
